\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}

\title{Impact of Smart Health Devices on Privacy}
\author{Team Members: Gaby Le Bideau, Jeffrey Kauv Li, \\ Susan Pan, Aybuke Ekiz}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This report investigates the privacy implications of the transition from traditional health trackers to connected smart health devices, with a particular focus on wearable technology such as Fitbit. Our goal is to understand how this technological evolution impacted user privacy and provide insights into the privacy assessments of such devices.
\end{abstract}

\section{Introduction}
The introduction of smart health devices has significantly altered the landscape of personal health monitoring, offering unprecedented insights into individual wellness. However, this technological advancement raises critical privacy concerns. This section will outline the context, objectives, and scope of our study.

\section{Research Methods}
Our methodology comprises four primary components designed to provide a comprehensive understanding of the privacy implications associated with smart health devices:

\subsection{Technical Literature Review}
Examining documentation, marketing materials, and technical specifications related to smart health devices to understand their design and functionality.

\subsection{Literature Search}
A systematic review of academic and industry literature was conducted to identify reported privacy concerns and breaches associated with these devices.

\subsection{Privacy Notices Review}
We analyzed privacy notices and relevant documents of smart health devices to assess how user data is collected, stored, and shared.

\subsection{Instrumentation and Monitoring}
Using network monitors and other tools, we tracked the data transmitted by these devices to identify potential privacy vulnerabilities.

\section{Results}
This section presents our findings, detailing the data collection practices of smart health devices, identified privacy threats, and their causes. We provide a comparative analysis of privacy policies and the actual data handling practices observed.

\section{Conclusions}
Our research highlights significant privacy concerns arising from the widespread adoption of smart health devices. We discuss the implications of our findings and suggest measures to mitigate privacy risks.

\section{Appendix}
 datasets, extended analyses, and technical documentation that support findings.

\section{Contributions}
\textit{Contributions.md}: This file documents the contributions of each team member to the project.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
